\pkg{digiRhythm}: an \proglang{R} package for rhythmicity assessment using the degree of functional coupling

### 2023-06-14 jstatsoft/article.Rnw
small changes in the complete text

%% - \author{} with primary affiliation (and optionally ORCID link)
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Hassan-Roland Nasser~\orcidlink{0000-0003-1821-3234}\\Agroscope - Digital Production
   \AND Marie Schneider~\orcidlink{0000-0003-4921-8353}\\Johann Heinrich von Th\"unen\\ Institute of Organic Farming
   \And Marianne Cockburn~\orcidlink{0000-0003-3193-0641}\\Agroscope - Equine Research Group}
\Plainauthor{Hassan-Roland Nasser, Marie Schneider, Marianne Cockburn}

@@

\Address{
  Hassan-Roland Nasser\\
  Agroscope, Digital Production\\
  Tanikon 1\\
  8352, Ettenhaussen \\
  Switzerland\\
  E-mail: \email{roland.nasser@agroscope.admin.ch, joa.stachowi@gmail.com}\\
  URL: \url{https://ch.linkedin.com/in/nasserha/, https://orcid.org/0000-0003-4921-8353}\\
  \newline

  Marie Schneider\\
  Johann Heinrich von Th\"unen Institute of Organic Farming\\
  Trenthorst 32\\
  23847 Westerau\\
  Germany \\
  \emph{and}\\
  University of Hohenheim –  Department of Livestock Systems Engineering\\
  Garbenstra{\ss}e 9 \\
  70599 Stuttgart\\
  Germany\\
  E-mail: \email{marie.schneider@thuenen.de}\\
  \newline

@@

\begin{document}
%\SweaveOpts{concordance=TRUE} %For some reason, this gives an error!

@@

\item \fct{sliding\_DI}: With this function, users can compute and graphically present the diurnality index, using a specific definitions of day/night per day.

@@

The DFC and HP can be calculated employing the \fct{dfc} function. A suggested workflow is outlined below. Once the data is loaded and its compatibility with the library is verified, the data—originally sampled at 1-minute intervals—is resampled to 15-minute intervals. In this context, 'resampling' refers to a simple summation process. For instance, if the dataset includes the number of steps recorded at 1-minute intervals, resampling to 15 minutes entails summing the steps taken during each 15-minute interval. Afterward, an activity is selected (in this example, we select the activity from the second column, i.e., motion index), and the DFC is calculated using the \fct{dfc} function as illustrated below:

@@

Although the \fct{dfc} function can accommodate data with any sampling frequency, several authors \citep{sinz1976systemanalyse, sarout2018assessment, fuchs2022detecting, scheibe1999comparative} have suggested that optimal insights can be achieved using a seven-day sliding window with a 15-minute sampling period. To maintain simplicity, the current version does not offer an option to alter the length of the sliding window (e.g., to 6, 8, or more days). However, this could potentially be implemented in future versions, if found to be useful.

@@

In this formula, $C_d$ and $C_n$ represent the sum of activity during the daytime and nighttime, respectively. $T_d$ and $T_n$ are the number of activity samples recorded during the daytime and nighttime. The number of samples is typically dependent on the sampling frequency. For instance, if activity is measured at 15-minute intervals, and daytime is defined as the period between 06:00 AM and 04:00 PM, then $T_d$ would be calculated as 4 samples per hour × 10 hours = 40 samples.

@@

In the above example for the \fct{diurnality} function, the day starts at 6:30 AM and ends at 4:30 PM, while the night starts at 6 PM and ends at 5 AM. Note that the \fct{sliding\_DI} function would compute the DI for each day in the dataset based on the specified day/night periods, of that day. This could provide a more accurate reflection of the individual's behavior, as it accounts for changes in daylight hours throughout the year.

>>>>

%% - \author{} with primary affiliation (and optionally ORCID link)
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Hassan-Roland Nasser~\orcidlink{0000-0003-1821-3234}\\Agroscope - Digital Production
   \AND Marie Schneider~\orcidlink{0000-0003-1073-7754}\\Johann Heinrich von Th\"unen\\ Institute of Organic Farming
   \And Marianne Cockburn~\orcidlink{0000-0003-3193-0641}\\Agroscope - Equine Research Group}
\Plainauthor{Hassan-Roland Nasser, Marie Schneider, Marianne Cockburn}

@@

\Address{
  Hassan-Roland Nasser\\
  Agroscope, Digital Production\\
  Tanikon 1\\
  8352, Ettenhaussen \\
  Switzerland\\
  E-mail: \email{roland.nasser@agroscope.admin.ch}\\
  URL: \url{https://ch.linkedin.com/in/nasserha/, https://orcid.org/0000-0003-1821-3234}\\
  \newline

  Marie Schneider\\
  Johann Heinrich von Th\"unen Institute of Organic Farming\\
  Trenthorst 32\\
  23847 Westerau\\
  Germany \\
  \emph{and}\\
  University of Hohenheim –  Department of Livestock Systems Engineering\\
  Garbenstra{\ss}e 9 \\
  70599 Stuttgart\\
  Germany\\
  E-mail: \email{marie.schneider@thuenen.de}\\
  URL: \url{https://orcid.org/0000-0003-1073-7754}
  \newline

@@

\begin{document}
\SweaveOpts{concordance=TRUE}
%\SweaveOpts{concordance=TRUE} %For some reason, this gives an error!

@@

\item \fct{sliding\_DI}: With this function, users can compute and graphically present the diurnality index, using specific definitions of day/night per day.

@@

The DFC and HP can be calculated employing the \fct{dfc} function. A suggested workflow is outlined below. Once the data is loaded and its compatibility with the library is verified, the data—originally sampled at 1-minute intervals—is resampled to 15-minute intervals. In this context, 'resampling' refers to a simple summation process. For instance, if the dataset includes the number of steps recorded at 1-minute intervals, resampling to 15 minutes entails summing the steps taken during each 15-minute interval. It is additionally possible to convert the timezone, if needed (not in this excample). Afterwards, an activity is selected (in this example, we select the activity from the second column, i.e., motion index), and the DFC is calculated using the \fct{dfc} function as illustrated below:

@@

Although the \fct{dfc} function can accommodate data with any sampling frequency, several authors \citep{sinz1976systemanalyse, sarout2018assessment, fuchs2022detecting} have suggested that optimal insights can be achieved using a seven-day sliding window with a 15-minute sampling period. To maintain simplicity, the current version does not offer an option to alter the length of the sliding window (e.g., to 6, 8, or more days). However, this could potentially be implemented in future versions, if found to be useful.

@@

In this formula, $C_d$ and $C_n$ represent the sum of activity during the daytime and nighttime, respectively. $T_d$ and $T_n$ are the number of activity samples recorded during the daytime and nighttime. The number of samples is typically dependent on the sampling frequency. For instance, if activity is measured at 15-minute intervals, and daytime is defined as the period between 06:30 AM and 04:30 PM, then $T_d$ would be calculated as 4 samples per hour × 10 hours = 40 samples.

@@

In the above example for the \fct{diurnality} function, the day starts at 6:30 AM and ends at 4:30 PM, while the night starts at 6 PM and ends at 5 AM. Note that the \fct{sliding\_DI} function would compute the DI for each day in the dataset based on the specified day/night periods, of that day. This could provide a more accurate reflection of the individual's behavior, as it accounts for changes daily routines, that externally control the organisms activity or changes in daylight hours throughout the year.
